### 2019-03-24 reports/thesis/chapters/5_inference.tex
Inference chapter
Edited inference chapter
Edited clim in defectExample
Edited xlim in DefectRadius

Disagreement between the scan and \texttt{aRTist} can be found by simply subtracting one image from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This statistic is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal. Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $Z_{x,y}$ statistics, assuming there are no defects, can be approximately quantified
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Whereas lower case $z$ denote a realisation or an observation of that random variable.

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data and was used to train the variance model, such as a Gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.

This method for inference was applied to the dataset \texttt{Sep16 120deg}. Here a cuboid with voids were purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}. The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there. The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist}.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of a 3D cuboid with voids}
  \label{fig:inference_testObject}
\end{figure}

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids. The $p$-values obtained were used for hypothesis testing using the \cite{benjamini1995controlling} procedure, controlling the FDR at the 5\% level. Pixels detected as positive are shown in red in d).}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

For each pixel, a $z$ statistic was calculated. A $z$ statistic too large in magnitude will classify that pixel as a positive result. In two-tailed hypothesis testing framework \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent $z$ statistic in a different way
\begin{equation}
  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
\end{equation}
which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.

@@

Model misspecification appeared to be the main source of error. The $z$ statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}. It can be seen that the majority of the $z$ statistics does not look Normal. Also the majority of the $p$-values does not look uniformly distributed. This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
    \caption{Histogram of $z$}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
    \caption{$p$-values}
    \label{fig:inference_inferenceIntro_pvalue}
  \end{subfigure}
}
  \caption{a) The histogram of the $z$ statistics is compared with the standard Normal distribution. The standard Normal distribution is known as the null distribution in this scenario. b) The $p$-values are ordered and plotted. The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure.}
  \label{fig:inference_inferenceIntro_histogram}
\end{figure}

This chapter recaps hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test. Assumptions used on the hypothesis testing can be relaxed by using the empirical null \citep{efron2004large}, which is reviewed here. The empirical null is then extended to an image filter, called the empirical null filter. This filter adjust each $z$ statistic according to its neighbours, ironing out false positive results. Simulations and results are shown towards the end of the chapter.

@@

Consider a $z$ statistic from a pixel. If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$. This can be described in another way by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$. A hypothesis test can judge how much $Z$ deviates from 0 by defining the alternative hypothesis $H_1:\mu\neq 0$. A statistic which does not have the null distribution is known as non-null.

In two-tailed hypothesis testing \cite{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice and was used throughout this thesis. Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.

Multiple hypothesis testing occurs when there are more than one hypothesis to test. For example $n$ pixels can be tested where the $z$ statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$. Let the corresponding $p$-values be $p_1, p_2, \cdots, p_n$.

The uncorrected test classify any $p_i<\alpha$ as positive. This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increase \citep{shaffer1995multiple}. This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. The number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}. Using the notation, PCER is defined as
\begin{equation}
  \text{PCER}=
  \dfrac{1}{n}
  \expectation[V]
  \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
\begin{equation}
  \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $n_0$\\
    Non-null & $T$ & $S$ & $n-n_0$\\\hline
    &$n-R$&$R$&$n$
  \end{tabular}
  \caption{Random variable definitions for true/false positives/negatives made in multiple hypothesis testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = 1-\prob(V=0) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$. Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negatives. This is because the correction traded too many false positives for false negatives.

@@

The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and choose different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is then adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\cdots,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue} the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.

@@

\begin{table}
    \centering
    \begin{tabular}{c|c}
        Correction&Controls for\\\hline
        No correction&$\text{PCER}\leqslant\alpha$\\
        Bonferroni&$\text{FWER}\leqslant\alpha$\\
        BH&$\text{FDR}\leqslant\alpha$
    \end{tabular}
    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
    \label{table:inference_corrections}
\end{table}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
      \caption{$z$ statistics}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
      \caption{Histogram of $z$ in sub-image}
    \end{subfigure}
    }
    \caption{The resulting $z$ image is shown in a). A $200\times 200$ sub-image was taken shown by the dashed lines. A histogram of the $z$ statistics in the sub-image is shown in b). The critical region was obtained by using the BH procedure at the 5\% FDR level.}
    \label{fig:inference_inferenceSubsample1_histogram}
\end{figure}

Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}. The distribution of the $z$ statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$. Almost half of the pixels were tested positive. It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.

@@

The null standard deviation was estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
\begin{equation}
  \ln p_{Z}(z) = 
  \ln\left[
    \dfrac{\pi_0}{\sqrt{2\pi}{\sigma}_0}
  \right]
  -\dfrac{1}{2}
  \left(
    \dfrac{z-{\mu}_0}{{\sigma}_0}
  \right)^2
  \ .
\end{equation}
Taking derivatives
\begin{equation}
  \dfrac{\partial}{\partial z} \ln p_{Z}(z) =
  -\left(
    \dfrac{
      z-{\mu}_0
    }
    {
      {\sigma}_0^2
    }
  \right)
\end{equation}
\begin{equation}
  \dfrac{\partial^2}{\partial z^2} \ln p_{Z}(z) =
  -\dfrac{
    1
  }
  {
    {\sigma}_0^2
  }
\end{equation}
which motivates the estimator \citep{efron2004large}
\begin{equation}
  \widehat{\sigma}_0 = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
    \right|_{z=\widehat{\mu}_0}
  \right]^{-1/2}
  \ .
\end{equation}
The evaluation of $z=\widehat{\mu}_0$ is used because at the mode, it was assumed that the null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.

This method does not need estimations of $\pi_0$ which makes it quite useful. The estimations of $\pi_0$ is discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}. \cite{efron2004large} motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.

@@

Return back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}. The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. The kernel density estimate \citep{parzen1962on} is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right) + 0.16
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range.

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
  \caption{The density of the $z$ statistics was estimated using a kernel density estimate. The dot dash lines shows the empirical null distribution multiplied by some constant, this is to insulate the two densities have the same curvature at the mode.}
  \label{fig:inference_inferenceSubsample1_densityEstimate}
\end{figure}

@@

The use of the kernel density estimate has its advantages. The only tuning parameter is the bandwidth $h$ and the density estimate is simple enough to do calculus on it. Speed may be an issue as an evaluation of the density estimate requires the sum over the $n$ $z$ statistics.

The $z$ statistics were normalised to $T_1,T_2,\cdots,T_n$ by using
\begin{equation}
  T_i = \dfrac{
    Z_i - \widehat{\mu}_0
  }
  {
    \widehat{\sigma}_0
  }
  \label{eq:inference_empiricalNullNormalise}
\end{equation}
for $i=1,2,\cdots,n$. The normalised $p$-values were obtained by using
\begin{equation}
  p_i = 2(1-\Phi(|t_i|))
\end{equation}
and then were used in the BH procedure. The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$. In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places. The critical region and the normalised $p$-values are shown in Figure \ref{fig:inference_inferenceSubsample1_nullResults}.

>>>>

Disagreement between the scan and \texttt{aRTist} can be found by subtracting one image from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal. Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Lower case $z$ denote a realisation or an observation of that random variable.

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data and was used to train the variance model, such as a gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.

This method for inference was applied to the dataset \texttt{Sep16 120deg}. A cuboid (4 cm $\times$ 4 cm $\times$ 6 cm) with voids was purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}. The voids were of various diameters 2.4 mm, 1.2 mm, 0.6 mm and 0.3 mm. 6 voids for each diameter were designed in the CAD. Voids with diameters 2.4 mm and 0.6 mm were regularly arranged, otherwise they were arranged irregularly. The precision of the manufacturing was in the order of $\pm0.1\text{ mm}$.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of a 3D cuboid with voids; the scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there. The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids. The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level. Pixels detected as positive are shown in red in d).}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

For each pixel, a test statistic was calculated. A test statistic too large in magnitude will classify that pixel as a positive result. In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
\begin{equation}
  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
\end{equation}
which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.

@@

Model misspecification appeared to be the main source of error. The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}. It can be seen that the majority of the test statistics does not look Normal. Also the majority of the $p$-values does not look uniformly distributed. This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
    \caption{Histogram}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
    \caption{$p$-values}
    \label{fig:inference_inferenceIntro_pvalue}
  \end{subfigure}
}
  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution. The standard Normal distribution is known as the null distribution in this scenario. b) The $p$-values are ordered and plotted. The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure. The dotted line shows the result if the $p$-values were uniformly distributed.}
  \label{fig:inference_inferenceIntro_histogram}
\end{figure}

This chapter recaps hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test. Assumptions used on the hypothesis testing can be relaxed by using the empirical null \citep{efron2004large}, which is reviewed here. The empirical null is then extended to an image filter, called the empirical null filter. This filter adjust each test statistic according to its neighbours, ironing out false positive results. Simulations and results are shown towards the end of the chapter.

@@

Consider a test statistic from a pixel. If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$. This can be described in another way by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$. A hypothesis test can judge how much $Z$ deviates from 0 by defining the alternative hypothesis $H_1:\mu\neq 0$. A statistic which does not have the null distribution is known as non-null.

In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice and was used throughout this thesis. Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.

Multiple hypothesis testing occurs when there are more than one hypotheses to test. For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$. Let the corresponding $p$-values be $p_1, p_2, \cdots, p_n$.

The uncorrected test classify any $p_i<\alpha$ as positive. This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}. This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. The number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}. Using the notation, PCER is defined as
\begin{equation}
  \text{PCER}=
  \dfrac{1}{n}
  \expectation[V]
  \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
\begin{equation}
  \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}[htp]
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $n_0$\\
    Non-null & $T$ & $S$ & $n-n_0$\\\hline
    &$n-R$&$R$&$n$
  \end{tabular}
  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypothesis testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = \prob(V\geqslant1) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$. Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negatives. This is because the correction traded too many false positives for false negatives.

@@

The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and choose different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is then adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\cdots,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.

@@

\begin{table}[htp]
    \centering
    \begin{tabular}{c|c}
        Correction&Controls for\\\hline
        No correction&$\text{PCER}\leqslant\alpha$\\
        Bonferroni&$\text{FWER}\leqslant\alpha$\\
        BH&$\text{FDR}\leqslant\alpha$
    \end{tabular}
    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
    \label{table:inference_corrections}
\end{table}

Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}. The distribution of the test statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$. Almost half of the pixels were tested positive. It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.

\begin{figure}[htp]
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
      \caption{Test statistics}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
      \caption{Histogram of test in sub-image}
    \end{subfigure}
    }
    \caption{The resulting $z$ image is shown in a). A $200\times 200$ sub-image was taken shown by the dashed lines. A histogram of the test statistics in the sub-image is shown in b). The critical region was obtained by using the BH procedure at the 5\% FDR level.}
    \label{fig:inference_inferenceSubsample1_histogram}
\end{figure}

@@

The null standard deviation is estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
\begin{equation}
  \ln p_{Z}(z) = 
  \ln\left[
    \dfrac{\pi_0}{\sqrt{2\pi}{\sigma}_0}
  \right]
  -\dfrac{1}{2}
  \left(
    \dfrac{z-{\mu}_0}{{\sigma}_0}
  \right)^2
  \ .
\end{equation}
Taking derivatives
\begin{equation}
  \dfrac{\partial}{\partial z} \ln p_{Z}(z) =
  -\left(
    \dfrac{
      z-{\mu}_0
    }
    {
      {\sigma}_0^2
    }
  \right)
\end{equation}
\begin{equation}
  \dfrac{\partial^2}{\partial z^2} \ln p_{Z}(z) =
  -\dfrac{
    1
  }
  {
    {\sigma}_0^2
  }
\end{equation}
which motivates the estimator \citep{efron2004large}
\begin{equation}
  \widehat{\sigma}_0 = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
    \right|_{z=\widehat{\mu}_0}
  \right]^{-1/2}
  \ .
\end{equation}
The evaluation of $z=\widehat{\mu}_0$ is used because at the mode, it was assumed that the null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.

This method does not need estimations of $\pi_0$ which makes it quite convenient. The estimations of $\pi_0$ is discussed in literature such as \cite{benjamini2000adaptive, pounds2003estimating, storey2003statistical, pounds2004improving, langaas2005estimating, durnez2014posthoc}. \cite{efron2004large} motives the use of the empirical null by investigating various types of false discovery rates \citep{storey2002direct, storey2003positive, efron2002empirical, efron2007size} which will not be discussed here.

@@

Return back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}. The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. The kernel density estimate \citep{parzen1962on} is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_z,\text{IQR}_z/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
  \caption{The density of the test statistics was estimated using a kernel density estimate. The dot dash lines show the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
  \label{fig:inference_inferenceSubsample1_densityEstimate}
\end{figure}

@@

The use of the kernel density estimate has its advantages. The only tuning parameter is the bandwidth $h$ and the density estimate is simple enough to do calculus on it. Speed may be an issue as an evaluation of the density estimate requires the sum over the $n$ test statistics.

The test statistics were normalised to $T_1,T_2,\cdots,T_n$ by using
\begin{equation}
  T_i = \dfrac{
    Z_i - \widehat{\mu}_0
  }
  {
    \widehat{\sigma}_0
  }
  \label{eq:inference_empiricalNullNormalise}
\end{equation}
for $i=1,2,\cdots,n$. The normalised $p$-values were obtained by using
\begin{equation}
  p_i = 2(1-\Phi(|t_i|))
\end{equation}
and then were used in the BH procedure. The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$. In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places. The critical region and the normalised $p$-values are shown in Figure \ref{fig:inference_inferenceSubsample1_nullResults}.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullHistogram.eps}
        \caption{Histogram of $z$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullPValues.eps}
        \caption{$p$ values}
    \end{subfigure}
    }
    \caption{The critical regions and $p$-values were adjusted using the empirical null in the sub-image example.}
    \label{fig:inference_inferenceSubsample1_nullResults}
\end{figure}
